\chapter*{攻读硕士期间发表的论文}
\markboth{攻读硕士期间发表的论文}{}
\addcontentsline{toc}{chapter}{攻读硕士期间发表的论文}
\begin{enumerate}[leftmargin=4ex, labelsep=1.5ex, itemsep=1ex, topsep=1ex,partopsep=1ex,parsep=0pt]
    \renewcommand{\labelenumi}{[\theenumi]}
    \item \textbf{Zhiyu Zhang}, Min Xu*, Guiqian Jiang, Jinyu Zhang, Dexiang Meng, Wenlong Chen, Yuliang Chen, and Changjing Hu.
    High-density racetrack memory based on magnetic skyrmion bags controlled by voltage gates[J]. 
    \textbf{Journal of Applied Physics}, 2022, 132(11): 113901. \textbf{(Q2, IF 2.877)}
    \item Min Xu*, \textbf{Zhiyu Zhang*}, Jinyu Zhang, Guiqian Jiang, Yuliang Chen, Wenlong Chen, and Changjing Hu.
    Current-driven magnetic skyrmion diodes controlled by voltage gates in synthetic antiferromagnets[J]. 
    \textbf{Applied Physics Letters}, 2023, 122(15): 152404. \textbf{(Q2, IF 3.971)}
    \item Min Xu*, Guiqian Jiang*, \textbf{Zhiyu Zhang}, Runshui Li, Dexiang Meng and Jinyu Zhang.
    Fast switching of magnetic vortex state under an alternating magnetic field[J]. 
    \textbf{Journal of Physics D: Applied Physics}, 2022, 55(32): 325303. \textbf{(Q2, IF 3.409)}
    \item Min Xu*, Guiqian Jiang*, \textbf{Zhiyu Zhang}, Jinyu Zhang, Changjing Hu, Wenlong Chen and Yuliang Chen.
    Irreversible switching of vortex core in Pac-man nanodisks induced by rotating magnetic fields[J]. 
    \textbf{Journal of Physics D: Applied Physics}, 2022, 56(5): 055301. \textbf{(Q2, IF 3.409)}
    \item Jinyu Zhang*, Min Xu*, \textbf{Zhiyu Zhang}, Guiqian Jiang, Dexiang Meng.
    Generation and steady motion of skyrmionium in racetracks under successive pulsed currents and magnetic fields[J]. 
    \textbf{Physics Letters A}, 2022, 451: 128433. \textbf{(Q2, IF 2.707)}
\end{enumerate}